%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage{fontawesome}
\usepackage{etaremune}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Luca Denti} \\ \vspace{1pt}
    % \small \faMobile~+39 366 483 7147 $|$
    \Letter~\href{mailto:ldenti92@gmail.com}{ldenti92@gmail.com} $|$
    \faHome~\href{https://ldenti.github.io}{ldenti.github.io} $|$
    \faGithub~\href{https://github.com/ldenti}{github.com/ldenti}
\end{center}

\section{Research Interests}
My research activity focuses on developing heuristics and tools for processing and analyzing sequencing data. My interests are in the field of transcriptome analysis (spliced alignment and alternative splicing events quantification) and genomic variations analysis (genotyping of SNPs and indels as well as structural variations discovery). In short, I really like bioinformatics and programming languages.

\section{Postions}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Postdoctoral Researcher}{March 2022 -- Present}
      {University of Milano - Bicocca}{Milan, Italy}
      \resumeItemListStart
        \resumeItem{Supervisor: Prof. Paola Bonizzoni}
      \resumeItemListEnd
    \resumeSubheading
      {Postdoctoral Researcher}{Sep. 2020 -- Feb. 2022}
      {Institut Pasteur}{Paris, France}
      \resumeItemListStart
        \resumeItem{Supervisor: Dr. Rayan Chikhi}
      \resumeItemListEnd
    \resumeSubheading
      {Research Fellowship}{Jan. 2020 -- Aug. 2020}
      {University of Milano - Bicocca}{Milan, Italy}
      \resumeItemListStart
        % \resumeItem{Project: ``Algorithms to detect alternative splicing events''}
        \resumeItem{Supervisor: Dr. Yuri Pirola}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Doctor of Philosophy in Computer Science}{Nov. 2016 -- Oct. 2019}
      {University of Milano - Bicocca}{Milan, Italy}
      \resumeItemListStart
      \resumeItem{Thesis: ``Algorithms for analyzing genetic variability from Next-Generation Sequencing data''}
      \resumeItem{Supervisors: Prof. Paola Bonizzoni, Dr. Raffaella Rizzi, Dr. Marco Previtali}
      \resumeItemListEnd
    \resumeSubheading
      {Master's Degree in Computer Science}{Nov. 2014 -- Oct. 2016}
      {University of Milano - Bicocca}{Milan, Italy}
      \resumeItemListStart
      \resumeItem{Thesis: ``A new algorithmic approach for the approximate alignment of a string to a graph''}
      \resumeItem{Supervisors: Prof. Paola Bonizzoni, Dr. Raffaella Rizzi}
      \resumeItemListEnd
    \resumeSubheading
      {Bachelor's Degree in Computer Science}{Oct. 2011 -- Oct. 2014}
      {University of Milano - Bicocca}{Milan, Italy}
      \resumeItemListStart
      \resumeItem{Thesis: ``Development of an enhanced Petri Net simulator''}
      \resumeItem{Supervisors: Dr. Luca Bernardinello, Prof. Lucia Pomello}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Awards}
 \begin{itemize}
    \small{
        \item Premio Giovani Talenti 2022, Università degli Studi di Milano - Bicocca
        \item Best Poster Award, RECOMB2018
    }
 \end{itemize}

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Professional partnership}{Nov. 2019}
      {University of Milano - Bicocca}{Milan, Italy}
      \resumeItemListStart
        \resumeItem{Computer Science Lab and DNA Analysis 2019}
      \resumeItemListEnd
    \resumeSubheading
      {Substitute teaching (8 hours) - Computer Science}{Dec. 2017}
      {High School ``B. Russell''}{Garbagnate Milanese, Italy}
    \resumeSubheading
      {Research collaboration}{2017}
      {University of Milano - Bicocca}{Milan, Italy}
      \resumeItemListStart
        \resumeItem{Pattern matching on pangenome}
        \resumeItem{Supervisor: Prof. Paola Bonizzoni}
      \resumeItemListEnd
    % \resumeSubheading
    %   {Activity of data entry on CRM}{2013}
    %   {Dos\&Donts S.r.l.}{Rho, Italy}
  \resumeSubHeadingListEnd

\section{Research projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PANGAIA: Pan-genome Graph Algorithms and Data Integration}{}
      {Funding: EU Horizon 2020, RISE Marie Skłodowska-Curie Action}{Role: administrative and research}
  \resumeSubHeadingListEnd

%   \resumeSubHeadingListStart
%     \resumeSubHeading
%       {}{}
%       {}{}
%   \resumeSubHeadingListEnd

\section{Open Source Software}
    \resumeSubHeadingListStart
      \resumeProjectHeading {\textbf{SVDSS} $|$ \emph{C++}}{\href{https://github.com/Parsoa/SVDSS}{github.com/Parsoa/SVDSS}}
      \resumeProjectHeading {\textbf{PingPong} $|$ \emph{C++}}{\href{https://github.com/Parsoa/PingPong}{github.com/Parsoa/PingPong}}
      \resumeProjectHeading {\textbf{ASGAL} $|$ \emph{C++, Python}}{\href{https://asgal.algolab.eu/}{asgal.algolab.eu}}
      \resumeProjectHeading {\textbf{MALVA} $|$ \emph{C++}}{\href{https://algolab.github.io/malva/}{algolab.github.io/malva}}
      \resumeProjectHeading {\textbf{Shark} $|$ \emph{C++}}{\href{https://github.com/AlgoLab/shark}{github.com/AlgoLab/shark}}
      \resumeProjectHeading {\textbf{MALVIRUS} $|$ \emph{Snakemake, Python, Bash}}{\href{https://algolab.github.io/MALVIRUS/}{algolab.github.io/MALVIRUS}}
      \resumeProjectHeading {\textbf{ppvcf} $|$ \emph{C++}}{\href{https://ldenti.github.io/ppvcf/}{ldenti.github.io/ppvcf}}
    \resumeSubHeadingListEnd

\section{Teaching}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Teacher}{}
      {University of Milano - Bicocca}{Milan, Italy}
      \resumeItemListStart
        \resumeItem{Algorithms and Data Structure - Laboratory, \textit{B.Sc.~in Computer Science} (a.y. 2021/2022)}
        \resumeItemListEnd
    \resumeSubheading
      {Seminars}{}
      {University of Milano - Bicocca}{Milan, Italy}
      \resumeItemListStart
        \resumeItem{Analysis and visualization of NGS data (Bioinformatics, \textit{M.Sc.~in Computer Science} (a.y. 2021/2022)}
        \resumeItem{Analysis and visualization of NGS data (Bioinformatics, \textit{M.Sc.~in Computer Science} (a.y. 2020/2021)}
        \resumeItem{FMD-Index and SMEMs (Bioinformatics, \textit{M.Sc.~in Computer Science} (a.y. 2017/2018)}
        \resumeItemListEnd
    \resumeSubheading
      {Teaching assistant}{}
      {University of Milano - Bicocca}{Milan, Italy}
      \resumeItemListStart
        \resumeItem{Programming Language Laboratory, \textit{B.Sc.~in Statistics} (a.y. 2019/2020)}
        \resumeItem{Foundations of Computer Science, \textit{M.S.~in Data Science} (a.y. 2019/2020)}
        \resumeItem{Design and Analysis of Algorithms, \textit{B.Sc.~in Computer Science} (a.y. 2016/2017, 2017/2018, 2018/2019, 2019/2020)}
        \resumeItem{Algorithms and Data Structure, \textit{B.Sc.~in Computer Science} (a.y. 2016/2017, 2019/2020)}
      \resumeItemListEnd
    \resumeSubheading
      {Supervision activities}{}
      {University of Milano - Bicocca}{Milan, Italy}
      \resumeItemListStart
        \resumeItem{Co-supervisor of 11 B.Sc.~theses in Computer Science}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Publications}
Joint first/last authors are indicated with *. Any preprint is marked with a \(\dagger\).
{\small
\begin{etaremune}
    \item \(\dagger\) L. Denti*, P. Khorsand*, P. Bonizzoni, F. Hormozdiari, R. Chikhi. Improved structural variant discovery in hard-to-call regions using sample-specific string detection from accurate long reads. bioRxiv (2022)

    \item S. Ciccolella*, L. Denti*, P. Bonizzoni, G. Della Vedova, Y. Pirola*, and M. Previtali*. MALVIRUS: an integrated web application for viral variant calling. BMC Bioinformatics (2022)

    \item P. Khorsand*, L. Denti*, Human Genome Structural Variant Consortium, P. Bonizzoni, R. Chikhi, F. Hormozdiari. Comparative genome analysis using sample-specific string detection in accurate long reads. Bioinformatics Advances (2021)

    \item L. Denti*, Y. Pirola*, M. Previtali*, T. Ceccato, G. Della Vedova, R. Rizzi, P. Bonizzoni. Shark: fishing relevant reads in an RNA-Seq sample. Bioinformatics (2020)

    \item S. Ciccolella, G. Bernardini, P. Bonizzoni, M. Previtali, G. Della Vedova. Triplet-based similarity score for fully multi-labeled trees with poly-occurring labels. Bioinformatics (2020)

    \item L. Denti*, M. Previtali*, G. Bernardini, A. Sch\"{o}nhuth, P. Bonizzoni. MALVA: genotyping by Mapping-free ALlele detection of known VAriants. Iscience (2019)

    \item S. Beretta, L. Denti, M. Previtali. Graph Theory and Definitions. Encyclopedia of Bioinformatics and Computational Biology (2019)

    \item S. Beretta, L. Denti, M. Previtali. Network Properties. Encyclopedia of Bioinformatics and Computational Biology (2019)

    \item L. Denti, R. Rizzi, S. Beretta, G. Della Vedova, M. Previtali, P. Bonizzoni. ASGAL: aligning RNA-Seq data to a splicing graph to detect novel alternative splicing events. BMC Bioinformatics (2018)

    \item S. Beretta, P. Bonizzoni, L. Denti, M. Previtali, R. Rizzi. Mapping RNA-seq data to a transcript graph via approximate pattern matching to a hypertext. International Conference on Algorithms for Computational Biology. Springer (2017)
\end{etaremune}
}

\section{Talks, Posters, Schools, and Visits}
  {\small
  \resumeSubHeadingListStart
      \resumeSubSubheading
      {\textbf{Invited talks:}}{}
      \begin{etaremune}
        \item Structural Variations Discovery from Specific Strings. Nov. 9, 2022. Comenius University (Tomas Vinar)
      \end{etaremune}
      \resumeSubSubheading
        {\textbf{Talks:}}{}
        \begin{etaremune}
            \item Comparative genome analysis using sample-specific string detection in accurate long reads. HiTSeq2021
            \item Comparative genome analysis using sample-specific string detection in accurate long reads. DSB2021
            \item Dynamic quasi-minimal perfect hash function for k-mers. DSB2020
            \item MALVA: genotyping by Mapping-free ALlele detection of known VAriants. BITS2019
            \item MALVA: genotyping by Mapping-free ALlele detection of known VAriants. RECOMBSEQ2019
            \item Mapping RNA-seq data to a transcript graph via approximate pattern matching to a hypertext. AlCoB2017
        \end{etaremune}
        \resumeSubSubheading
        {\textbf{Posters:}}{}
        \begin{etaremune}
            \item MALVA: genotyping by Mapping-free ALlele detection of known VAriants. RECOMB2019
            \item ASGAL: aligning RNA-Seq data to a splicing graph to detect novel alternative splicing events. RECOMB2018
        \end{etaremune}
        \resumeSubSubheading
        {\textbf{Research visits:}}{}
        \begin{etaremune}
            \item Geneton (Bratislava, Slovakia). Dr. Tomas Szemes - Aug/Nov, 2022
            \item Institut Pasteur (Paris, France). Dr. Rayan Chikhi - Dec, 2019
            \item Centrum Wiskunde \& Informatica (Amsterdam, The Netherlands). Prof. Leen Stougie - Feb/Apr, 2019
            \item Centrum Wiskunde \& Informatica (Amsterdam, The Netherlands). Prof. Alexander Sch\"{o}nhuth - Oct/Dec, 2018
        \end{etaremune}
        \resumeSubSubheading
        {\textbf{Schools:}}{}
        \begin{etaremune}
            \item Intensive School on Cellular Automata (ACRI school) / Como (Italy) / 2018
            \item International School on Mathematics (Graph Theory, Algorithms and Applications) / Erice (Italy) / 2017
        \end{etaremune}
    \resumeSubHeadingListEnd
}

\section{Professional Activities}
\resumeSubHeadingListStart
    \resumeSubheading
      {Commitee}{}
      {Organizing commitee member of:}{}
      \resumeItemListStart
        \resumeItem{PhD School ``Introduction to Pangenomics'' 2022}
      \resumeItemListEnd
    \resumeSubheading
      {Reviewer}{}
      {Journals:}{}
      \resumeItemListStart
        \resumeItem{Algorithms for Molecular Biology / Bioinformatics / F1000Research / Nucleic Acids Research}
      \resumeItemListEnd
    \resumeSubSubheading
      {Conferences:}{}
      \resumeItemListStart
        \resumeItem{APBC 2022 / BIBM 2022,2018 / BICOB 2018 / ICCS 2017 / ISBRA 2021,2020,2018 / ITAT 2021 / RECOMB 2021 / RECOMB-CG 2022 / RECOMBSEQ 2022,2021 / SPIRE 2017 / WABI 2022,2020,2019}
      \resumeItemListEnd
\resumeSubHeadingListEnd


\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Python, Rust, Java, Bash, \LaTeX} \\
     \textbf{Frameworks}{: Snakemake} \\
     \textbf{Developer Tools}{: Git, Docker} \\
     \textbf{Libraries}{: biopython, gffutils, pysam, pandas, NumPy, Matplotlib, Seaborn}
    }}
 \end{itemize}

\section{References}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Prof. Paola Bonizzoni}{, University of Milano - Bicocca \hfill \href{mailto:paola.bonizzoni@unimib.it}{paola.bonizzoni@unimib.it}}\\
     \textbf{Dr. Rayan Chikhi}{, Institut Pasteur \hfill \href{mailto:rayan.chikhi@pasteur.fr}{rayan.chikhi@pasteur.fr}}\\
     \textbf{Prof. Alexander Sch\"{o}nhuth}{, University of Bielefeld \hfill \href{mailto:aschoen@cebitec.uni-bielefeld.de}{aschoen@cebitec.uni-bielefeld.de}}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
